---
title: |
  Taylor & Francis Rmarkdown template for authors (\LaTeX\-based 
  \textsf{Interact} layout + Chicago author-date reference style)
type: Course Project
author:
  - name: Beining Wu
    affil: 1
    email: andrewwu@mail.ustc.edu.cn
affiliation:
  - num: a
    address: |
      Department of Statistics and Finance, University of Science and Technology of China, Hefei, 230026
abstract: |
  Remains
keywords: |
  Remains
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage{xeCJK}
output: rticles::tf_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preliminaries

```{r}
data <- read.csv(file = "data.csv", head=TRUE, fileEncoding = "UTF8")
attach(data)
library(mapchina)
library(tidyverse)
library(sf)
library(fitdistrplus)
```

# Data Overview
First we take a glance at the distrbution of the `rent` variable. d`
```{r}
head(data)
summary(data)
hist(rent, breaks = "scott", main = "Histogram of Rent", xlab = "Monthly Rent Price", ylab = "Frequency", freq = FALSE)
lines(density(rent))
```


# Fitting

From the histogram plot we may hypothesis that the distribution is gamma.
```{r}
library(fitdistrplus)
library(MASS)
fit.gamma <- fitdist(rent, distr = "gamma", method = "mle")
summary(fit.gamma)
plot(fit.gamma)
```


# Mean Unit Value in Each District

Now we consider the mean rent in each district.
```{r}

unit <- data$rent/data$area

mean_unit_reg <- c(mean(unit[region=="东城"]),mean(unit[region=="西城"]),mean(unit[region=="昌平"]),mean(unit[region=="大兴"]),mean(unit[region=="房山"]),mean(unit[region=="怀柔"]),mean(unit[region=="门头沟"]),mean(unit[region=="密云"]),mean(unit[region=="平谷"]),mean(unit[region=="顺义"]),mean(unit[region=="通州"]),mean(unit[region=="延庆"]),mean(unit[region=="朝阳"]),mean(unit[region=="丰台"]),mean(unit[region=="海淀"]),mean(unit[region=="石景山"]))


mean_unit_reg[is.na(mean_unit_reg)]=0
```

And we can visualize as follows.

```{r}
df <- china %>%
        filter(Name_Province == "北京市")

ggplot(data = df) +
        geom_sf(aes(fill = rank(mean_unit_reg))) +
        scale_fill_distiller(palette = "BuPu", direction = 1) +
        theme_bw() +
        theme(legend.position = "none")
```

From the map we know that the unit price is significantly **higher** when location is more central. Now the

# Mean Unit Value and Subway 

```{r}
boxplot(rent~subway, main="Boxplot of Rent, Grouing by Subway")

```
